Dynein project log

### 2017-02-07 thesis_stuff/thesis_stuff.tex
fix typo in latex file
Thesis: Add another paper to thesis_stuff.tex.

>>>>

\subsection{Helix sliding in the stalk coiled coil of dynein couples ATPase and microtubule binding}
Discuss how other work has shown that MT affinity is controlled by registry. They do this study in vivo, and show that there is a coupling between ATPase activity and MT binding which is destroyed by locking the coiled coils into registries.

\textbf{Key findings}
\begin{itemize}
\item CC being unlocked is necessary for MT-affinity sensitivity to ATP, showing ATP-state influences MT-affinity
\item high MT affinity causes high ATPase rate, low MT affinity causes low ATPase rate (presumably bc ATP cannot bind)
\end{itemize}

WT: No ATP -> strong binding, ATP: weak binding\\
Locked in a register: ATP insensitivity\\
MT increases ATPase rate 25x\\
MT doesn't increase locked-register ATPase rate\\
(Thus unlocked registers are necessary for ATPase/MT-binding coupling)\\

They then did a FRET study to show that locking a registry \textit{induces} a change in linker conformation, pre/poststroke.\\

They provide the following explanation of dynein mechanochemical cycle:

\begin{itemize}
\item (apo): strong MT-binding, in $\alpha$ conformation
\item (ATP binding): causes a shift towards the $\Beta+$ conformation, causing MT dissociation by lowering affinity
\item (before ATP hydrolysis): dynein performs prestroke, \textit{then} hydrolyzes ATP
\item (during Phosphate or ADP release): MTBD rebinds to MT, returns to $\alpha$ registry, increasing the rate of product release, increasing MT affiniy, AND causing the powerstroke
\item (full release): turns back to apo dynein
\end{itemize}

ATPase and MT cycles are interestingly coupled.

\textbf{ATPase cycle}
\begin{itemize}
\item apo $\rightarrow$ ATP: this is somehow influenced by MT state
\item ATP $\rightarrow$ ADP+Pi: This happens after prestroke, somehow coupled to it or no?
\item ADP+Pi $\rightarrow$ ADP: This ejection (or the ADP ejection) is sped up by MTBD rebinding
\item ADP $\rightarrow$ apo: This ejection doesn't do anything structurally, according to Cianfrocco model
\end{itemize}
